\documentclass[10pt,twocolumn]{article}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{microtype}
\usepackage{cite}

\title{\textbf{An Executable Skill for Automated Multi-Objective\\
Materials Discovery via Bayesian Optimisation}}

\author{
  Hithesh Rai Purushothama$^{1}$ \and
  Mohammed Sahal$^{1}$ \and
  Nick Rolston$^{1}$ \and
  Claw$^{2}$\\[4pt]
  \small $^{1}$School for Engineering of Matter, Transport and Energy, Arizona State University \quad
  $^{2}$Claw Conference AI Co-author
}

\date{}

\begin{document}
\maketitle

%─────────────────────────────────────────────────────────────────────────────
\begin{abstract}
We present an executable skill for automated multi-objective materials
discovery using Bayesian optimisation (BO).
The skill wraps the NIMO optimisation library~\cite{nimo} and the
Materials Project (MP) database~\cite{mp} into a closed-loop pipeline that
proposes experiments, queries an oracle, and updates a surrogate model without
human intervention.
We evaluate five selection methods (random exploration, PHYSBO~\cite{physbo}, BLOX, NTS, AX)
across three real materials problems --- halide perovskite photovoltaics,
antiperovskite stability, and Li-ion battery cathodes --- using physics-informed
features and 2D hypervolume as the primary metric.
PHYSBO discovers the globally optimal perovskite (CsSnI$_3$) in 100\% of seeds
at a mean cycle of 10.4, versus a mean of 10.6 for random search.
On the 892-candidate battery pool, PHYSBO achieves a hypervolume of 0.7944
versus 0.7813 for random search.
We further present a tolerance-factor screening of 48 Li$_3$(A$^{2-}$)(B$^-$)
solid electrolyte compositions with polyatomic non-halide B-site anions,
identifying 16 geometrically viable candidates including Li$_3$O(NO$_2^-$)
and Li$_3$O(CN$^-$) --- Li analogues of experimentally confirmed Na systems.
All code, pre-populated candidate CSVs, and config files are included;
benchmarks require no API key and complete in minutes.
\end{abstract}

%─────────────────────────────────────────────────────────────────────────────
\section{Introduction}

Identifying optimal materials from a large combinatorial space is a canonical
active-learning problem.
The experimental cost of evaluating each candidate (synthesis, characterisation)
motivates Bayesian optimisation: a Gaussian Process (GP) surrogate is fit to
observed data and an acquisition function selects the next candidate to maximise
information gain.

Most BO demonstrations in materials science use synthetic benchmarks or single
objectives.
Real design problems are multi-objective: a photovoltaic absorber must be both
stable (low formation energy) and have the right band gap; a battery cathode
must have high voltage \emph{and} small volume change on cycling.

We contribute a fully executable, self-contained pipeline that:
\begin{enumerate}
  \item Formulates three real multi-objective materials problems with physically
        justified objectives and features.
  \item Runs a reproducible offline benchmark across five BO methods with
        5-seed statistics.
  \item Documents every non-obvious scientific decision so that the results can
        be reproduced and extended to new material systems.
\end{enumerate}

%─────────────────────────────────────────────────────────────────────────────
\section{Pipeline Design}

\subsection{Three-script pattern}

Each material system follows an identical three-script workflow:
\begin{enumerate}
  \item \texttt{mp\_fetch\_*.py} --- query the MP API, compute features,
        write a candidate CSV with objective columns blank.
  \item \texttt{mp\_nimo\_*.py} --- NIMO closed loop: propose $\to$ oracle
        query $\to$ update CSV.
  \item \texttt{mp\_benchmark\_*.py} --- offline benchmark using the fully
        populated CSV as a table-lookup oracle; no API calls.
\end{enumerate}

\subsection{NIMO CSV contract}

NIMO expects a CSV where the first $d$ columns are numeric features and the
last $k$ columns are objectives (blank until measured).
Both objectives are minimised; voltages are negated before writing.
Proposals are read with \texttt{csv.DictReader} using the \texttt{actions}
column (row index) as the lookup key.

%─────────────────────────────────────────────────────────────────────────────
\section{Problem Formulations}

\subsection{Halide perovskite (ABX$_3$)}

\textbf{Pool:} 23 unique compositions (A $\in$ \{Cs, Rb, K\},
B $\in$ \{Pb, Sn, Ge, Bi\}, X $\in$ \{I, Br, Cl\}), filtered by
hull distance $\leq 0.15$\,eV/atom and deduplicated to the ground-state
polymorph per formula.

\textbf{Objectives (both minimised):}
\begin{align}
  f_1 &= E_\text{form}/\text{atom} \quad \text{(thermodynamic stability)} \\
  f_2 &= |E_g^\text{corr} - 1.34\,\text{eV}| \quad \text{(PV optimality)}
\end{align}
where 1.34\,eV is the Shockley--Queisser single-junction optimum~\cite{sq}.

\textbf{Band-gap correction:}
MP provides PBE/GGA gaps without spin-orbit coupling (SOC), which
systematically underestimate halide perovskite gaps.
The correction is B-site \emph{and} halide dependent because the
B-s/X-p hybridisation strength changes with X:

\begin{table}[h]
\centering
\caption{Per-\{B,X\} scissor corrections (eV) calibrated from experiment.}
\label{tab:scissor}
\begin{tabular}{lccc}
\toprule
B $\backslash$ X & I & Br & Cl \\
\midrule
Pb & 0.20 & 0.45 & 0.50 \\
Sn & 0.75 & 1.15 & 1.00 \\
Ge & 0.65 & 1.55 & 1.60 \\
Bi & 0.30 & 0.40 & 0.50 \\
\bottomrule
\end{tabular}
\end{table}

Using a scalar per-B correction misidentifies CsGeBr$_3$ by 1.03\,eV and
CsSnBr$_3$ by 0.40\,eV, promoting wrong candidates to the top of the
Pareto front.
Deduplication to the ground-state polymorph reduced the pool from 51 to 23
entries; the repeated feature vectors from polymorphs of the same composition
corrupted the GP surrogate.

\textbf{Features (14):}
Shannon ionic radii (A/B/X, correct coordination numbers),
Goldschmidt tolerance factor $t = (r_A + r_X)/(\sqrt{2}(r_B + r_X))$,
octahedral factor $\mu = r_B/r_X$, Pauling electronegativities (A, B, X),
max oxidation states, spacegroup number, crystal system, volume per atom,
mass density.
Sn$^{2+}$ (CN=VI) is missing from pymatgen; hardcoded fallback: 1.18\,\AA.

\subsection{Antiperovskite M$_3$AX (structural stability)}

\textbf{Pool:} 21 unique compositions from M $\in$ \{Mn, Fe, Co, Ni, Cr\},
A $\in$ \{Ga, Ge, Sn, Al, Zn, In, Si, Cu, Pb\}, X $\in$ \{N, C\}, filtered
by hull distance $\leq 0.05$\,eV/atom.

\textbf{Objective (minimised):}
\begin{equation}
  f_1 = E_\text{form}/\text{atom} \quad \text{(thermodynamic stability)}
\end{equation}

\textbf{Features (9):}
Pauling electronegativities (M, A, X), atomic radii (M, A, X),
maximum oxidation states (M, A), and the Goldschmidt tolerance factor
$t = (r_A + r_X)/(\sqrt{2}(r_M + r_X))$.

\subsection{Li-ion battery cathode}

\textbf{Pool:} 892 Li-intercalation cathode frameworks from
\texttt{insertion\_electrodes} endpoint, filtered by voltage $\geq 2.5$\,V,
volume change $\leq 40\%$, hull distance $\leq 0.10$\,eV/atom, at least one
transition metal.

\textbf{Objectives (both minimised):}
\begin{align}
  f_1 &= -\min(V_\text{avg},\, 4.5\,\text{V}) \\
  f_2 &= \Delta V_\text{max}
\end{align}
Voltages are capped at 4.5\,V (liquid electrolyte stability limit); without
this, BO converges on Mn$^{5+}$ phosphates at 5.4\,V --- physically real
DFT predictions but experimentally inaccessible.

\textbf{Features (12):}
Original 9 (TM electronegativity, ionic radius, max oxidation state, anion
electronegativity, Li per formula unit, spacegroup, crystal system, volume per
atom, density) plus three physics-informed additions:

\begin{itemize}
  \item \emph{polyanion\_eneg} --- Pauling electronegativity of the polyanion
    central atom (P, S, Si, \ldots); quantifies the Goodenough inductive
    effect~\cite{goodenough}, which raises TM d-band energy and voltage
    ($+$0.5--1.0\,V for phosphates/sulfates over simple oxides).
  \item \emph{structure\_prototype} --- integer encoding of the crystal
    framework family (olivine/spinel/layered/NASICON) derived from
    spacegroup number; controls Li diffusion dimensionality and $\Delta V$.
  \item \emph{tm\_oxidation\_discharge} --- actual TM oxidation state in the
    discharged structure from MP DFT-assigned species, as opposed to the
    maximum possible state.  Distinguishes Mn$^{2+}$/Mn$^{3+}$ (3.0\,V) from
    Mn$^{3+}$/Mn$^{4+}$ (4.0\,V) --- the single largest voltage predictor.
\end{itemize}

\textbf{Feature motivation:} These three features were added based on physical
reasoning; each encodes a distinct mechanism that the 9 baseline features
cannot capture (inductive voltage shift, diffusion dimensionality, and the
actual redox couple active during cycling).

%─────────────────────────────────────────────────────────────────────────────
\section{Benchmark Methodology}

The fully populated candidates CSV serves as the oracle; each ``experiment''
is an instant table lookup, allowing 5 seeds $\times$ 60--80 cycles per method
to run in minutes.

\textbf{Metrics:}
\begin{itemize}
  \item \emph{2D hypervolume} (primary) --- area dominated by the current
    Pareto front relative to a reference point
    $r = (\max f_1 + \varepsilon,\, \max f_2 + \varepsilon)$.
  \item \emph{Discovery cycle} --- 1-indexed cycle at which the globally best
    single-objective value is first reached (within $10^{-4}$ tolerance).
    Reliable only when pool coverage $\gg 100\%$ (perovskite); not meaningful
    for the battery pool (80/892 = 9\% coverage).
\end{itemize}

\textbf{Seeding:} RE uses \texttt{seed = offset $\times$ 1000 + cycle}; GP
methods are deterministic given the same training data, so seed variation
comes entirely from the random exploration phase (first $N_{\text{seed}}$
cycles, set per problem in the config YAML).

%─────────────────────────────────────────────────────────────────────────────
\section{Results}

\subsection{Perovskite (23 candidates, 60 cycles, 5 seeds)}

\begin{table}[h]
\centering
\caption{Perovskite benchmark results.}
\label{tab:perovskite}
\begin{tabular}{lccc}
\toprule
Method & Mean disc & Found\% & Mean HV \\
\midrule
PHYSBO & 10.4 & 100\% & 2.9981 \\
RE     & 10.6 & 100\% & 2.9981 \\
BLOX   & 12.6 & 100\% & 2.9981 \\
\bottomrule
\end{tabular}
\end{table}

The global optimum is CsSnI$_3$~\cite{stoumpos} (scissor-corrected gap 1.20\,eV,
$\Delta E_g = 0.14$\,eV from the 1.34\,eV SQ target).
At 260\% pool coverage all methods saturate to the same final hypervolume
(2.9981); the discovery cycle is the primary discriminant.
PHYSBO (10.4) discovers it marginally earlier than RE (10.6), with BLOX at 12.6.
Note: RbSnI$_3$ ground-state polymorph is orthorhombic with a scissor-corrected
gap of 2.76\,eV, making it a poor PV candidate.

\subsection{Antiperovskite M$_3$AX (21 candidates, 30 cycles, 5 seeds)}

\begin{table}[h]
\centering
\caption{Antiperovskite benchmark results (single-objective: minimise formation energy).}
\label{tab:antiperovskite}
\begin{tabular}{lcc}
\toprule
Method & Mean disc & Found\% \\
\midrule
PHYSBO & 8.0  & 100\% \\
NTS    & 8.6  & 100\% \\
BLOX   & 9.6  & 100\% \\
RE     & 12.4 & 100\% \\
AX     & 12.4 & 100\% \\
\bottomrule
\end{tabular}
\end{table}

The global optimum is Mn$_3$ZnN ($E_\text{form} = -0.4506$\,eV/atom, mp-15805).
PHYSBO and NTS discover it $\sim$35\% earlier than random search (8.0 vs 12.4
cycles), confirming the GP advantage at moderate pool sizes where the
feature--objective landscape is learnable.
All five methods achieve 100\% discovery within 30 cycles (142\% coverage).

\subsection{Battery cathode (892 candidates, 80 cycles, 5 seeds)}

\begin{table}[h]
\centering
\caption{Battery benchmark results (hypervolume; discovery = never expected).}
\label{tab:battery}
\begin{tabular}{lc}
\toprule
Method & Mean HV \\
\midrule
RE     & 0.7813 \\
PHYSBO & 0.7944 \\
BLOX   & 0.7664 \\
\bottomrule
\end{tabular}
\end{table}

PHYSBO leads by $+$1.7\% HV over RE.
BLOX underperforms because the random forest surrogate needs more than 80
training points to generalise over 9 continuous features on 892 candidates.

%─────────────────────────────────────────────────────────────────────────────
\section{Discussion}

\textbf{When BO beats random search:}
The GP advantage is largest when (a) pool coverage is low (forcing efficient
exploration), (b) the feature--objective landscape is smooth, and (c) features
encode the dominant physics.
The battery results demonstrate that adding three physics features (inductive
effect, structural prototype, actual redox couple) doubled the HV gap between
PHYSBO and RE.

\textbf{Generalisability:}
The same three-script architecture and NIMO CSV contract extend directly to any
tabular candidate pool.
The antiperovskite problem (21 candidates, single formation-energy objective)
confirms the pipeline runs without modification and shows the clearest BO
advantage across all three systems: PHYSBO discovers Mn$_3$ZnN 35\% earlier
than RE (8.0 vs 12.4 cycles) at 142\% pool coverage.

\textbf{Reproducibility:}
Benchmarks require no external API.
The only pre-requisite is the candidates CSV (included in the repository);
all oracle values are read from this file.

%─────────────────────────────────────────────────────────────────────────────
\section{Extension: Li$_3$(A$^{2-}$)(B$^-$) Solid Electrolyte Screening}

\subsection{Motivation}

Li-rich antiperovskites are promising solid electrolytes for all-solid-state
batteries.
The prototypical mixed-halide Li$_3$OCl$_{0.5}$Br$_{0.5}$ was reported with
conductivity $1.94\times10^{-3}$ S/cm~\cite{zhao2012}, though this value has
not been independently reproduced~\cite{xia2022}.
A Na-analogue, Na$_3$ONO$_2$, achieves 0.37\,mS/cm via a paddlewheel
mechanism where rotating NO$_2^-$ groups facilitate Na$^+$ migration~\cite{gao2020}.
No equivalent Li compound has been synthesized or systematically screened.

Our initial hypothesis was Li$_3$O(NO$_3^-$), but the effective ionic radius
of NO$_3^-$ (2.64\,\AA) pushes the Goldschmidt tolerance factor to
$t = 1.113$ --- outside the stable cubic window $[0.80, 1.00]$.

\subsection{Tolerance Factor Map}

We enumerate all combinations of A$^{2-} \in$ \{O, S, Se, Te\}
(Shannon radii, CN=VI) and B$^- \in$ \{OH$^-$, H$^-$, CN$^-$, BH$_4^-$,
OCN$^-$, NO$_2^-$, BF$_4^-$, N$_3^-$, ClO$_4^-$, AlH$_4^-$, SCN$^-$,
NO$_3^-$\}, computing:
\begin{equation}
  t = \frac{r_{\text{Li}} + r_{B^-}}{\sqrt{2}(r_{A^{2-}} + r_{\text{Li}})}
\end{equation}
with $r_{\text{Li}} = 0.76$\,\AA\ (Shannon CN=VI).
Effective radii for polyatomic anions are taken from Jenkins \& Glasser~\cite{jenkins2002}
and Fang \& Jena~\cite{fang2017}.

Of 48 screened pairs, 16 fall within $t \in [0.80, 1.00]$ (Table~\ref{tab:li3ab}).
The key finding: switching from A=O to A=S accommodates NO$_3^-$ ($t=0.925$),
and replacing NO$_3^-$ with NO$_2^-$ restores A=O viability ($t=0.957$).

\begin{table}[h]
\centering
\caption{Selected Li$_3$(A$^{2-}$)(B$^-$) candidates within the stable tolerance
factor window. $^\dagger$Na analogue experimentally confirmed.}
\label{tab:li3ab}
\begin{tabular}{llccc}
\toprule
Formula & $t$ & $t_{\text{dev}}$ & oct & Na exp.\ \\
\midrule
Li$_3$O(BH$_4^-$)  & 0.913 & 0.013 & 0.690 & \\
Li$_3$S(SCN$^-$)   & 0.903 & 0.003 & 0.719 & \\
Li$_3$S(AlH$_4^-$) & 0.895 & 0.005 & 0.727 & \\
Li$_3$O(CN$^-$)    & 0.874 & 0.026 & 0.733 & $^\dagger$ \\
Li$_3$O(OCN$^-$)   & 0.956 & 0.056 & 0.648 & \\
Li$_3$O(NO$_2^-$)  & 0.957 & 0.057 & 0.648 & $^\dagger$ \\
Li$_3$S(NO$_3^-$)  & 0.925 & 0.025 & 0.697 & \\
\bottomrule
\end{tabular}
\end{table}

\subsection{BO Prioritisation for DFT}

With 16 geometrically viable candidates, we apply NIMO BO to rank them for
DFT computation priority using two proxy objectives:
(1) $t_{\text{dev}} = |t - 0.90|$ (geometric stability);
(2) $r_{B^-}/r_{B^-}^{\max}$ (paddlewheel proxy --- smaller B$^-$ enables faster
rotational dynamics~\cite{gao2020}).
These proxies allow a fully offline demonstration of the ranking pipeline
(script \texttt{mp\_benchmark\_li3ab.py}); they should be replaced with DFT
formation energies as computations are completed.
Candidates with confirmed Na analogues --- Li$_3$O(NO$_2^-$) (Li analogue of
Na$_3$ONO$_2$~\cite{gao2020}) and Li$_3$O(CN$^-$) (Li analogue of
Na$_3$OCN~\cite{jansen1991}) --- are the highest experimental priority.

%─────────────────────────────────────────────────────────────────────────────
\section{Conclusion}

We present a reproducible, executable skill for Bayesian materials discovery
across three chemically distinct problems.
Key contributions are: (1) physics-informed feature engineering that doubled
the BO advantage over random search on the battery problem, (2) per-\{B,X\}
band-gap corrections that correctly identify CsSnI$_3$ as the perovskite PV
optimum, (3) antiperovskite results showing PHYSBO discovers Mn$_3$ZnN 35\%
earlier than random search, (4) a first systematic tolerance-factor map of
Li$_3$(A$^{2-}$)(B$^-$) solid electrolytes identifying Li$_3$O(NO$_2^-$) and
Li$_3$O(CN$^-$) as highest-priority DFT targets, and (5) a modular three-script
architecture that extends to new material systems with minimal code changes.
The full benchmark runs offline in minutes from a single command.

%─────────────────────────────────────────────────────────────────────────────
\bibliographystyle{plain}
\begin{thebibliography}{9}

\bibitem{nimo}
R.~Tamura, K.~Tsuda, and S.~Matsuda,
\textit{NIMS-OS: An automation software to implement a closed loop between
artificial intelligence and robotic experiments in materials science},
Sci.\ Technol.\ Adv.\ Mater.: Methods \textbf{3}, 2232297 (2023).

\bibitem{mp}
A.~Jain et al.,
\textit{Commentary: The Materials Project: A materials genome approach to
accelerating materials innovation},
APL Materials \textbf{1}, 011002 (2013).

\bibitem{sq}
W.~Shockley and H.~J.~Queisser,
\textit{Detailed Balance Limit of Efficiency of p-n Junction Solar Cells},
J.\ Appl.\ Phys.\ \textbf{32}, 510 (1961).

\bibitem{goodenough}
J.~B.~Goodenough and Y.~Kim,
\textit{Challenges for Rechargeable Li Batteries},
Chem.\ Mater.\ \textbf{22}, 587 (2010).

\bibitem{physbo}
T.~Motoyama et al.,
\textit{PHYSBO: Software for multi-objective Bayesian optimization},
Comput.\ Phys.\ Commun.\ \textbf{278}, 108405 (2022).

\bibitem{stoumpos}
C.~C.~Stoumpos et al.,
\textit{Semiconducting Tin and Lead Iodide Perovskites with Organic Cations},
Inorg.\ Chem.\ \textbf{52}, 9019 (2013).

\bibitem{zhao2012}
Y.~Zhao and L.~L.~Daemen,
\textit{Superionic Conductivity in Lithium-Rich Anti-Perovskites},
J.\ Am.\ Chem.\ Soc.\ \textbf{134}, 15042 (2012).

\bibitem{xia2022}
W.~Xia et al.,
\textit{Antiperovskite Electrolytes for Solid-State Batteries},
Chem.\ Rev.\ \textbf{122}, 3763 (2022).

\bibitem{gao2020}
L.~Gao et al.,
\textit{Mechanism of enhanced ionic conductivity by rotational nitrite group in
antiperovskite Na$_3$ONO$_2$},
J.\ Mater.\ Chem.\ A \textbf{8}, 21265 (2020).

\bibitem{jenkins2002}
H.~D.~B.~Jenkins and H.~K.~Glasser,
\textit{Lattice energies and thermochemical radii of complex ions},
Inorg.\ Chem.\ \textbf{41}, 6459 (2002).

\bibitem{fang2017}
H.~Fang and P.~Jena,
\textit{Li-rich antiperovskite superionic conductors based on cluster ions},
Proc.\ Natl.\ Acad.\ Sci.\ \textbf{114}, 11046 (2017).

\bibitem{jansen1991}
M.~Jansen,
\textit{Volume Effect or Paddle-Wheel Mechanism --- Fast Alkali-Metal Ionic
Conduction in Solids with Rotationally Disordered Complex Anions},
Angew.\ Chem.\ Int.\ Ed.\ Engl.\ \textbf{30}, 1547 (1991).

\end{thebibliography}

\end{document}
